---
execute:
  echo: false
---

# TEACHING DOSSIER

```{r echo = FALSE}
library(tidyverse)
evals_tib <- here::here("data/evals.csv") |> readr::read_csv()
```



Teaching is a profound passion of mine, particularly when it allows me to apply my research findings in the classroom. My teaching experience spans K-25 in both public and private high schools in BC and Alberta; internationally as an assistant language teacher in Japan; and in both undergraduate and graduate courses in higher education. I have taught a diverse range of subjects in K-12, including physical education, digital media studies, outdoor education, sports medicine, science, English, and math.

At the University of Victoria, I co-designed and taught three online undergraduate courses: Learning Design, Distributed and Open Learning, and Social Media and Personalized Learning. These courses use WordPress as the primary hub of networked interactions, enabling students to personalize their web presence while acquiring critical digital literacy skills by engaging with the open web. (see my 2022 proceedings on multi-section course design (Irvine et al., 2022) as an example of how I share my practice in scholarly venues).

One of the highlights of my undergraduate teaching experience was co-designing and teaching in parallel with a fellow Ph.D. student during the early stages of the global COVID-19 pandemic. This collaborative process was mutually supportive and helped us navigate the complexities of teaching undergraduates in an innovative, technology-integrated context. Our experience is documented in a presentation at the OTESSA21 conference at the Congress of the Social Sciences and Humanities. I also co-designed and taught Coaching for Transformational Blended Learning and have been contracted to revise Theory and Practice of Adult Education, courses in the Graduate Certificate in Adult Learning: Coaching and Facilitation at TWU. These courses take an experiential approach to coaching individual learners and facilitating group processes in educational contexts. At the undergraduate level at TWU, I collaborated with an instructional designer to create an introductory online course called Learning with Technology which enrolled its first learners in the Fall of 2024. This course helps learners understand the affordances of technology for sense-making in learning environments by teaching them a technology-integrated workflow that maintains their personal privacy and teaches learners how to build networks of knowledge and learning using WordPress.

## TEACHING EFFECTIVENESS

The following is a table summarizing courses I have taught, including a synopsis of learner ratings of their experience with me as their instructor. Note that several courses did not meet the threshold for reporting ratings as there were too few submissions of learner experience surveys.

```{r}
knitr::kable(evals_tib)
```



## Approach to Teaching

## Efforts to Improve Teaching

## Contributions to Teaching and Student Learning


<!--



```{r}
freq_tbl_evals <- evals_tib |>
  dplyr::group_by(Term) |> 
  dplyr::summarise(
    frequency = n()
  )
freq_tbl_evals
```
```{r}
datawizard::describe_distribution(x = evals_tib,
  select = NULL,
  exclude = NULL,
  centrality = "mean",
  dispersion = TRUE,
  iqr = TRUE,
  range = TRUE,
  quartiles = FALSE,
  include_factors = FALSE,
  ci = NULL)
```
-->
